\documentclass[10pt, a4paper, fleqn]{article}
\usepackage{listings}
\usepackage{color}
\usepackage{fullpage}
\usepackage[ampersand]{easylist}
\usepackage[parfill]{parskip}
\usepackage{subfiles}



%\definecolor{dkgreen}{rgb}{0,0.6,0}
%\definecolor{gray}{rgb}{0.5,0.5,0.5}
%\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  %numberstyle=\tiny\color{gray},
  %keywordstyle=\color{blue},
  %commentstyle=\color{dkgreen},
  %stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}

\renewcommand{\labelenumii}{\Alph{enumii}}
\renewcommand{\labelenumiv}{\alph{enumiv}}
\ListProperties(Numbers1=a, Numbers2=L, Numbers3=r, Numbers4=l, Numbers5=R, FinalMark={)}, Progressive*=.5cm, Hide2=1, Hide3=2, Hide4=3, Hide5=4, Hide6=5, Style*=)


\begin{document}

\pagenumbering{gobble}
\subfile{TitlePage} \newpage


\section*{Acknowledgement}
This project would not have been possible without the guidance and the help of several individuals
who in one way or another contributed and extended their valuable assistance in the preparation
and completion of this assignment.

I express utmost gratitude to my Computer Science teachers – Ms. Nishat Khimani, Ms. Manaali Dubal, and Mr. Siddharth Naidu
whose inputs and encouragement have been my inspiration as I hurdled over all the obstacles in the completion of this project. 
I would also like to thank them for providing valuable inputs and feedback to aid us in our project.

Furthermore, I thank all the members of my family who always had a kind concern and consideration regarding all my project and 
academic requirements and were helpful all through the project. I specially thank my father whose inputs regarding the details of
this project were very valuable and helpful given his eye for detail. I also thank my mother, who helped sand off the rough edges
of the project, giving feedback and suggestions regarding the aesthetic part of the project.
\newpage

\tableofcontents
\newpage


\pagenumbering{arabic}


\subfile{ArrayFill} \newpage
\subfile{CharCount} \newpage
\subfile{Dec_Bin_Oct_Hex} \newpage
\subfile{BoundaryElementSort_Sum} \newpage
\subfile{DateInWords} \newpage
\subfile{DeterminantSolver} \newpage
\subfile{PseudoArithmeticSeries} \newpage
\subfile{HarshadNum} \newpage
\subfile{KaprekarNum} \newpage
\subfile{MobiusFn} \newpage
\subfile{GCDLCMRecursive} \newpage
\subfile{NoteDispense} \newpage
\subfile{NumToWords} \newpage
\subfile{PrimesInArray} \newpage
\subfile{QuickSortArray} \newpage
\subfile{RevStr} \newpage
\subfile{CharacterCountWithoutLoop} \newpage
\subfile{SpecialNum} \newpage
\subfile{SaddlePoint} \newpage
\subfile{SieveOfErasthosenes} \newpage
\subfile{ASCIIDecryption} \newpage
\subfile{MergeSortArray} \newpage
\subfile{PhoneDirectory} \newpage
\subfile{StudentRecords} \newpage
\subfile{SmartSubstring} \newpage
\subfile{DuplicateCharCount} \newpage
\subfile{SymmetrixDiagonalSum} \newpage
\subfile{CalendarGenerator} \newpage
\subfile{MatrixInSpiral} \newpage
\subfile{CircularPrime} \newpage
\subfile{CharTypePercentage} \newpage
\subfile{ReverseEachWord} \newpage
\subfile{BouncyIncDecCheck} \newpage
\subfile{StringNegativeEncoder} \newpage
\subfile{NoOfDays} \newpage
\subfile{WondrousSquare} \newpage
\subfile{MatrixMultiplication} \newpage
\subfile{TowersOfHanoi} \newpage
\subfile{Unique2DigitCombos} \newpage
\subfile{2DArraySort} \newpage
\subfile{MatrixMirror} \newpage
\subfile{MatrixRotation90} \newpage
\subfile{InsertionSortArray} \newpage
\subfile{RecursiveBinarySearch} \newpage
\subfile{DecimalRoman} \newpage
\subfile{LinkedList} \newpage
\subfile{QueueAsLL} \newpage
\subfile{StackAsLL} \newpage
\subfile{QuickSortLinkedList} \newpage
\subfile{BinaryTree} \newpage



\subfile{OtherResources} \newpage

\end{document}